Language and vision in conceptual processing: Multilevel analysis and statistical power

### 2022-11-04 manuscript/manuscript.Rmd
typo busting

While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding two of them.

@@

While the variables are generally described in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.

>>>>

While the variables are outlined in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.

@@

While the variables are outlined in the [\underline{general introduction}](#present-studies), a few further details are provided below regarding some of them.

### 2022-11-04 manuscript/manuscript.tex
typo busting

While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding two of them.

@@

While the variables are generally described in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.

>>>>

While the variables are outlined in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.

@@

While the variables are outlined in the \protect\hyperlink{present-studies}{\underline{general introduction}}, a few further details are provided below regarding some of them.
